Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble

### 2022-06-01 docs/paper/paper.Rmd
switch to incidence rate based scoring

```{r load-functions}
source(here("R", "utils.R"))
source(here("R", "coverage-plots.R"))
```

@@

- Visualise forecasts across time horizons in examplar countries.
- Weighted interval score.
- Calibration and coverage.
- Relative interval score.
- Relative interval score overall, distribution of scores, by horizon both overall and distribution, by location overall and distribution.
- Relative interval score by interval range by horizon
- Calibration at 50 and 90 credible intervals
- Coverage across intervals.

@@

```{r coverage}
coverage <- scores |>
  copy() |>
  DT(, horizon := as.character(horizon)) |>
  DT(, coverage_deviation := NULL) |>
  add_coverage(ranges = ranges, by = c("model", "horizon")) |>
  summarise_scores(fun = signif, digits = 2, by = c("model", "horizon")) |>
  melt(
    measure.vars = patterns("coverage_"), variable.name = "range",
    value.name = "coverage"
  )|>
  DT(, range := gsub("coverage_", "", range)) |>
  DT(, range := paste0(range, "% interval"))
```

```{r relative-interval-score}
cols <- c("location", "target_end_date", "horizon", "range", "model")
relative_interval_score <- scores |>
  copy() |>
  setorderv(cols) |>
  DT(, c(..cols, "interval_score")) |>
  unique() |>
  DT(,
    relative_interval_score := interval_score / shift(interval_score),
    by = c("location", "target_end_date", "horizon", "range")
  ) |>
  DT(model %in% "Surrogate")
```

@@

@@

```{r plot-coverage, fig.height = 12, fig.width = 18, out.width = "95%"}
(
  (
    (
      plot_coverage_range(coverage, ranges) /
      plot_rel_score_by_quantile(relative_interval_score)
    )  +
    plot_layout(heights = c(3, 1), guides = "collect")
  ) |
  plot_coverage_quantiles(scores)
) +
  plot_layout(guides = "collect", widths = c(1, 2)) +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.margin = margin()
  )
```

>>>>

```{r load-functions}
source(here("R", "utils.R"))
source(here("R", "evaluate.R"))
source(here("R", "coverage-plots.R"))
```

@@

- Visualise forecasts across time horizons in examplar countries.
- Weighted interval score on incidence rate per 10,000 people to account for population differences between locations.
- Calibration and coverage.
- Relative interval score.
- Relative interval score overall, distribution of scores, by horizon both overall and distribution, by location overall and distribution.
- Relative interval score by interval range by horizon
- Calibration at 50 and 90 credible intervals
- Coverage across intervals.

@@

```{r coverage}
coverage <- calc_coverage(scores)
```

```{r relative-interval-score}
relative_interval_score <- scores |>
  calc_relative_score(
    cols = c("location", "target_end_date", "horizon", "range")
  )
relative_wis <- scores |>
  summarise_scores(
    by = c("location_name", "target_end_date", "horizon", "model")
  ) |>
  calc_relative_score(cols = c("location_name", "target_end_date", "horizon"))
```

@@

```{r}
relative_wis |>
  copy() |>
  ggplot() +
  aes(x = relative_interval_score) +
  geom_vline(xintercept = 1, linetype = 2) +
  geom_density() +
  facet_wrap(vars(horizon)) +
  scale_x_continuous(trans = "log")
```

```{r plot-eval, fig.height = 12, fig.width = 18, out.width = "95%"}
 (
  (
    (
      plot_rel_wis(coverage, ranges) /
      plot_rel_wis_by_horizon(relative_wis)
    )  +
    plot_layout(heights = c(3, 1), guides = "collect")
  ) |
  plot_rel_wis_by_location(relative_wis)
) +
  plot_layout(guides = "collect", widths = c(2, 1)) +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.margin = margin(),
    legend.justification = "centre"
  )
```

@@

```{r plot-coverage, fig.height = 12, fig.width = 18, out.width = "95%"}
 (
  (
    (
      plot_coverage_range(coverage, ranges) /
      plot_rel_score_by_quantile(relative_interval_score)
    )  +
    plot_layout(heights = c(3, 1), guides = "collect")
  ) |
  plot_coverage_quantiles(scores)
) +
  plot_layout(guides = "collect", widths = c(1, 2)) +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.margin = margin(),
    legend.justification = "centre"
  )
```
